My Cool Title

### 2019-05-04 paper.tex
Added section describing the pomdp implementation

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}

@@

>>>>

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{siunitx}

@@

The output from the POMDP model's training process is a policy file that defines the best location to place the next search waypoint based on the device's current state.
This state is tracked by the device during run-time by recording the device's previous search locations and previous waypoint positions, which is done by disretising the world into a $6\times6$ grid and setting the relevant grid unit's $v$ value.
Each grid square represents a \SI{35}{\degree} angular translation, encompassing a \SI{210}{\degree}$times$\SI{210}{\degree} field of view. 
This setup gives the state access to perfectly observable $n$ and $v$ parameters, while the observation parameter $o$ is generated by the object detector.

When the user moves the device into a new grid square by rotating the device past \SI{35}{\degree}, thereby making a new $v$ observation and changing the state, or observes a new object, the device triggers the controller to generate a new waypoint location.
The controller uses the new state observation $\omega$ to update its belief state and queries the policy for the best location to place the new waypoint. 
The policy output is an action from the action set $\mathbf{A}$ that specifies the next adjacent grid square to place the waypoint.
For example, an `UP' output would result in the waypoint being placed one grid square, i.e. \SI{35}{\degree}, above where the current grid square within view.
